Time Series Bootstrapping For Solar Current

### 2021-12-06 deliverables/paper.Rmd
Added EDA functions, day segmenting code

>>>>

```{r data}
df <- read_csv("../data/final/irradiance_full_final.csv")
```

# EDA

```{r timeseries}

#' Plot a timeseries of a single variable
#'
#' @param df A dataframe containing `variable`
#' @param variable A string referring to a column of `df`
#' @param n_days The number of days (starting from the
#'    beginning of the data) to plot
#' @return A ggplot object of a timeseries of `variable` for `n_days` days
time_series_of_var <- function(df, variable, n_days) {
ret_plot <- df %>%
  mutate(date = lubridate::make_datetime(Year, Month, Day, Hour, Minute)) %>%
  head(24 * n_days) %>%
  ggplot() +
  geom_line(aes_string(x = "date", y = variable)) +
  theme_bw()
return(ret_plot)
}

time_series_of_var(df, "GHI", 6)
time_series_of_var(df, "current_out", 6)
```

```{r hour-plot}

#' Plot the values of `variable` at each hour of the day
#'
#' @param df A dataframe containing `variable`
#' @param variable A string referring to a column of `df`
#' @return A ggplot object of a boxplot of `variable` segmented by hour
hour_plot_of_var <- function(df, variable) {
df$Hour <- as.factor(df$Hour)
ret_plot <- df %>%
  ggplot() +
  geom_boxplot(aes_string(x = "Hour", y = variable)) +
  xlab("Hour (0-23)") +
  ylab(paste("Distribution of", variable)) +
  theme_bw()
return(ret_plot)
}

hour_plot_of_var(df, "GHI")
hour_plot_of_var(df, "current_out")
```

# Data filtering

```{r filter}
HOUR_WINDOW <- 11:16
df_high_irradiance <- df[df$Hour %in% HOUR_WINDOW,]
filtered_current_hist <- ggplot() +
  geom_histogram(aes(x = df_high_irradiance$current_out)) +
  theme_bw()
print(filtered_current_hist)
```

# Bootstrapping

```{r functions}

np <- function(x, l) {
  n <- length(x)
  print(n)
  # l <- n %/% b
  # b <- n %/% l
  b <- floor(n / l)
  print(b)
  print(n / b)
  blocks <- matrix(NA, nrow = b, ncol = l)
  for (i in 1:b) {
    # blocks[i, ] <- x[(i - 1) * l + 1:(i * l)]
    print(x[(i - 1) * l + 1:(i * l)])
  }
  return(blocks)
}

nbb <- function(x, l) {
  B <- 10000
  b <- floor(length(x) / l)
  theta_hat_star_nbb <- rep(NA, B)
  # nb_blocks <- np(x, l, b)
  nb_blocks <- np(x, l)
  for (i in 1:B) {
    # sample blocks
    idx <- sample(1:b, b, replace = TRUE)
    theta_hat_star_nbb[i] <- mean(x[idx, ])
  }
  ggplot() +
    geom_histogram(aes(theta_hat_star_nbb))

  st.d <- sd(theta_hat_star_nbb)
  bias <- mean(theta_hat_star_nbb) - mean(x)

  print(paste(
    "The standard deviation with ", l, " blocks is: ", st.d, ". \n The bias is: ",
    bias
  ))
}
```

```{r sampling}
# B1 <- df[df$Hour == c(7:10),]$current_output # Hours before peak
# B2 <- df[df$Hour == c(11:14),]$current_output # Peak hours
# B3 <- df[df$Hour == c(15:18),]$current_output # Hours after peak

nbb(hours, 4) # in order to make b blocks I would need to solve for b = [n/l] (floor) where n is the length of our data and l is 4, so make nbb call l instead of b

nbb(hours, 12)

# Could also block instead by hours but by total current output. Peak hours would be a frame around the highest output and then hours before and after would coincide with that. This would cause the hours to potentially be different based on the season/month as months that get dark earlier could see peak hours earlier in the day.

# dpeak <- c(B1,B2,B3)
```
